---
# Comments work up here as well
# Metadata Section in YAML
# very space and placement rigid
title: "R Markdown Primer"
author: "Erico Cardelli Author"
# Lets make a larger directive for output: we need to go to the next line and tab indent
output: 
    html_document:
        #Table of Contents
        toc: yes
---

# References

## R markdown link to topic notebook


[Class OneNote](https://onedrive.live.com/edit.aspx/Documents/Combined%20Notes?cid=7e1da892b45794cd&id=documents&wd=target%28Technical%2FTraining.one%7CE6348C5D-083C-4A40-8324-D42F0B525693%2FR%20Markdown%20Primer%7C6ED37784-C83D-4E14-B84B-54A6BCD399EC%2F%29
onenote:https://d.docs.live.net/7e1da892b45794cd/Documents/Combined%20Notes/Technical/Training.one#R%20Markdown%20Primer&section-id={E6348C5D-083C-4A40-8324-D42F0B525693}&page-id={6ED37784-C83D-4E14-B84B-54A6BCD399EC}&end)


### Be Contextually aware

After your metadata section do a "metasetr" which will feed new metadata into new global settings

```{r}
# Now a snippet to set things right
# its funny that outside of this block a comment is a giant Title

# This and by using autotab, I was able to piece out
# knitr::options for chunks then
# RMarkdown is rendering
# knitr is evaluating
# and the $ is for functions in the knitr opts_chunk function SET (whatever,otherstuff,etc)
knitr::opts_chunk$set(cache=TRUE, fig.align = 'center', echo = TRUE)
```


# My First Section

We start a new section with a single HASHTAG and this is the first paragraph in that section.  Notice how the text wraps around to the next line in the editor but it still has the same line number and that's pretty cool.  That's because all text on a single line is considered a paragraph.

Leaving a blank line starts a new paragraph.  Remember Markdown is highly spaced and cased aware.
If you don't leave a blank line you are still in the same paragraph

So it is very important to pay attention to spaces.

F7 for spell check.

# New Section

You start a new section by leaving a blank line and then starting the next line with a hash tag.  No need to close the previous section, just start a new one. (Similar to La-Tex)

# Subsections

Creating a subsection is easy.  Two Hash tags

## This is a Subsection

We start a section in a section to start it

You can use add decorator module

## Another Subsection

Same rules apply no need to close previous subsection just keep a blank line in between them

the output type is actually an R function you are specifying and is in the R Markdown Package

# Back to Sections

# Formatting Text

One Underline is for _Emphasized_ 

_Emphasized Words Go Here_

Strong Text is with two underlines __Strong__

__Strong Text Goes Here__

And you can combine them with Three Underlines ___Bold and Strong___

And finally code snippets are the BACKTIC under the Esc

`This is computer Code`

# Lists

## Unordered List

Fruit

- Apple
- Orange
- Banana
- Mango
- Durian
- Watermellon
- Dragonfruit

## Ordered List

To createa an ordered list use 1. at the beginning of your list items
Hit Dice
and a sublist with a. to make the sublist

### Sublists

I added subs in there too

1. Bug
    a. gnat
    a. fly
    a. spider
    a. wasp
1. Fool
    i. dope
    i. idiot
1. Knight
1. Troll
1. Dragon

# Links

You put the text you want displayed in square brackets and then the url into parenthesis

`[Google](https://www.google.com)` = [Google](https://www.google.com)

[Class OneNote](https://onedrive.live.com/edit.aspx/Documents/Combined%20Notes?cid=7e1da892b45794cd&id=documents&wd=target%28Technical%2FTraining.one%7CE6348C5D-083C-4A40-8324-D42F0B525693%2FR%20Markdown%20Primer%7C6ED37784-C83D-4E14-B84B-54A6BCD399EC%2F%29
onenote:https://d.docs.live.net/7e1da892b45794cd/Documents/Combined%20Notes/Technical/Training.one#R%20Markdown%20Primer&section-id={E6348C5D-083C-4A40-8324-D42F0B525693}&page-id={6ED37784-C83D-4E14-B84B-54A6BCD399EC}&end)


# R Time!!!!

_Alt+Ctrl+I for new code chunk_


```{r}
1+1
```

R Markdown showed you the code, executed cleanly, and displays results

```{r}
# this is a comment inside of R code
# here I will set a variable that is only inside this code bubbles
x<-3
x
```

# Text in between code?  Such Heresy

```{r THISISHOWTONAMEACODEBLOCK}
x*2
```

Chunks are cumulative and serial but not in any way related to the console or any other `ENVIRONMENT`

# Naming Chunks?

So in the code chunk right after the r that defines it as `R Code` put a space and then a name followed by the other curlybrace
See the Example here

```{r C0d3_N@me-3x@mp73}
x*7+3
```

Lets show the results of a code chunk without showing the code

```{r another-example,echo=FALSE}
5*x+4
```

by doing echo=false the code is safely hidden but results flow

look to the left and you can see carrots that let you fold the stuffs

## Better Examples

Alt+Shift+K will show you keyboard Shortcuts

# Plots

Plots all make sense of data
but first we have to prepare for the plots
And loading more prerequisites


```{r load ggplot2}
library(ggplot2)
```

Put the library code alone to enable smart reuse

```{r}
ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point()
```

_What is amaziing about this is that the picture is embeded as a graphic but its encoded so anyone can see it and all the images are embedded_

# Including Javascript

The web page actually embeds everything for your use

# Plot Improvements

I want to center the plot...

```{r Align-my-diamonds-plot,fig.align='center'}
ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point()
```

The alignment directive in that code was easy to figure out with the comma intellisyntax

## A Caption

```{r plot-diamond-with-caption,fig.align='center',fig.cap='A scatterplot of diamond price vs. size, color coded according to diamond cut',cache=TRUE}

ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point()


```

Lots to unpack in this code...
but where it sayd cache=TRUE, that means that if this code snippet hasn't changed use it as is. possibly saving a lot of time

